---
title: "Compound Poisson Distribution"
author: "Vahid Meimand"
Date: "10/18/2018"
runtime: shiny
output: ioslides_presentation
fontsize: 8pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outline

- App Summary
- Statistical Background
- Results

## App Summary
This application illustrates how a combination of poisson and gamma distributions can be used to calculate the total rain fall in a year or the total loss amount for an insurance policy over a given period.

In both cases the number of occurances is simulated with a Poisson distrubution with the mean number of occurances, $\lambda$.  The severity/magnitude of events has been simulated using a Gamma distribution with shape parameter, $\alpha$ and the rate parameter,$\beta$.

Note, that the mean and variance of the magnitude has the following relationship to the rate and shape parameters: $$\mu = \alpha / \beta$$$$\sigma^2 = \alpha / \beta^2$$



## Statistical Background
Here is an illustration of the Poisson and Gamma Distributions:
```{r,fig.width=4, fig.height=2,, tidy=TRUE}
inputPanel(
  column(6,
         sliderInput("n_breaks","number of bins", 
                     step=1,min=5, max=100, value = 20),
         numericInput("lambda", label = "Lambda:",
                      min = 1, max = 100, value = 3)),
  column(6,
         numericInput("alpha", label = "Alpha:",
                      min = 1, max = 20000, value = 20),
         numericInput("beta", label = "Beta:",
                      min = 1, max = 1000, value = 10)
  )
)
column(6,
renderPlot({
  set.seed(1)
  events_ct <<- rpois(10000,input$lambda)
  hist(events_ct, probability = TRUE, breaks = as.numeric(input$n_breaks), 
       xlab = "Duration (minutes)", main = "Poisson histogram")
  }))

column(6,
       renderPlot({
         set.seed(1)
         events_sev <<- rgamma(10000,input$alpha,rate=input$beta)
         hist(events_sev, probability = TRUE, breaks =
              as.numeric(input$n_breaks), 
              xlab = "Duration (minutes)", main = "Poisson histogram")
  }))
```



## Results
Here after performing 10000 simulations for total annual rainfal based on the parameters specified in the previous slide, the following histogram is resulted:
```{r}
renderPlot({
       hist(events_sev*events_ct, probability = TRUE, breaks =
              as.numeric(input$n_breaks), 
              xlab = "total annual rainfall", main = "Histogram for total annual rainfall for 10000 simlations")
  })
```

## Summary
Here is a summary of the simulated raifalls
```{r, echo=T}
renderText({
  summary(events_sev*events_ct)})
```


<br><br>
The files are all available in git repo:
https://github.com/vahidzm/RprodFinalProj
